Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-11-08 thesis.Rmd
verkar ej funka på det viset
lyckats sortera ut så att jag visar tabellerna där jag vill att de ska visas

# Ethics

@@

@@

>>>>

## Ethics

@@

```{r sample-characteristics, echo=FALSE}
sample.characteristics.table
```

@@

```{r BE-subofi, echo=FALSE}
print(p)
```

Table 5

```{r SBP-subofi, echo=FALSE}
print(pSBP)
```

Table 6 - Subofi detailed

```{r SBP-subofi-detailed, echo=FALSE}
print(pd)
```

```{r BE-subofi-detailed, echo=FALSE}
print(pSBPd)
```

print(sample.characteristics.table)
print(sample.characteristics.tableBE)
print(sample.characteristics.tableSBP)
print(log_regBE_sample.characteristics.table)
print(log_regSBP_sample.characteristics.table)
print(log_regBE_sample.characteristics.table_unadjusted)
print(log_regSBP_sample.characteristics.table_unadjusted)
